---
output: rmarkdown::github_document
---
  
  
# *Alpine salamander* Supplementary Info Shiny app  

This is the repository with digital Supplementary Information for the alpine salamander paper [title peding].
You can clone this entire repository and run the app locally. RStudio project is built with [`renv`](https://rstudio.github.io/renv/){target="_blank"} package manager.  

## How to install

### Clone the repository

If you have git available on your computer, run git command below.

```{git, eval=FALSE, echo=TRUE}
git clone https://github.com/MirzaCengic/atra-app.git
```

Otherwise, you can download zip file of the project, including data and packages.

[INCLUDE SCREENSHOT]  

Open RStudio project file `atra-app.RProj`. First you will need to set up packages with `renv`.  

Run code below to install package if needed.

```{r eval=FALSE, echo=TRUE}
if (!requireNamespace("remotes"))
  install.packages("remotes")

remotes::install_github("rstudio/renv")
```

Then setup packages.  

```{r}
# Use renv::init() to initialize a project. renv will discover the R packages used in your project, 
# and install those packages into a private project library.
renv::init()
```

## How to run

To run the app, open script `R/run_app.R`. This script will source scripts with initial setup, and Shiny app user interface and backend setup. If script `R/app_setup.R` is sourced sucessfuly, this means that the app should work right away. 

Run function `runApp()` to attempt launching the browser with the app.   
